%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer II, Content Engineering} % Job title
    {Saks Fifth Avenue} % Organization
    {New York, NY} % Location
    {Sep. 2017 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Wrote high-performance JavaScript, modular CSS, and semantic HTML5.}
       \item {Built and deployed helpful internal automation tools.}
	   \item {Provided mentorship and support to two junior devs.}
	   \item {Exercised project management skills, facilitating interaction between key departments.}
	   \item {Daily meetings and project collaboration with remote workers in multiple time zones.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {Guardian News \& Media} % Organization
    {New York, NY} % Location
    {Aug. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a complex, multi-month web feature for the high-profile Amazon web series \textit{The Grand Tour}.}
        % https://www.theguardian.com/tour-tracker/ng-interactive/2016/dec/02/grand-tour-uk-italy-dodge-hellcat-venice
        % https://www.theguardian.com/tour-tracker
        \item {Built 14 pages from scratch: a mainpage hub, an interactive world map, and 12 extended weekly features.}
        % \item {Implemented a mobile-first, fully responsive approach.}
        \item {Quickly absorbed internal written documentation; seamlessly adopted The Guardian’s custom development workflow.}
        \item {Gracefully adjusted to changes in project timeline and scope.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer I, Content Engineering} % Job title
    {Saks Fifth Avenue} % Organization
    {New York, NY} % Location
    {Jun. 2016 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Primary editorial developer with a focus on animation and user interaction.}
       \item {Unique web experiences required close multi-departmental communication and collaboration.}
       \item {Standardized the team's development framework using Node and Gulp.js.}
       \item {Developed a widely-used internal knowledge wiki.}
      \end{cvitems}
    }    

%---------------------------------------------------------
  \cventry
    {Content Producer} % Job title
    {Saks Fifth Avenue} % Organization
    {New York, NY} % Location
    {Aug. 2014 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the creation, scheduling, and maintenance of all static web content.}
        % \item {Maintained a fast-paced content rollout schedule.}
        \item {Built a shared library of Ruby scripts to automate complex and otherwise time-consuming tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Intern} % Job title
    {HDTracks.com} % Organization
    {New York, NY} % Location
    {Aug. 2012 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented innovative and effective bi-weekly email newsletters.}
        \item {Expansive subscriber base (200,000+) left no margin for error.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
